Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-08 xrb2/paper.tex
Added some text and velocity at t=50 ms in flame propagation section

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:flame_speeds} Flame speed and acceleration values measured for each 
	simulation. {\color{blue}$v_0$} is the flame velocity {\color{blue}in the $+r$ direction} at $t 
	= 0$. The initial flame 
	velocities and accelerations are derived from a quadratic least-squares fit to each of the 
	datasets for times $t \gtrsim 20~\mathrm{ms}$.}
	\tablehead{\colhead{run} & \colhead{$v_0$ (cm s$^{-1}$)} & \colhead{$a$ (cm s$^{-2}$)}} 
	\startdata
  {\tt F1000}     & $(3.38 \pm 0.11) \times 10^5$ & $(-0.43 \pm 1.57) \times 10^5$ \\
  {\tt F500}      & $(2.66 \pm 0.27) \times 10^5$ & $(10.97 \pm 3.22) \times 10^5$ \\
  {\tt F500\_2E8} & $(3.98 \pm 0.19) \times 10^5$ & $(-1.56 \pm 2.63) \times 10^5$ \\
  {\tt F500\_3E8} & $(-4.56 \pm 2.92) \times 10^5$ & $(3.39 \pm 0.60) \times 10^7$ \\
	\enddata
	%
\end{deluxetable}

@@

Figure~\ref{fig:flame_speeds_1} gives position vs.\ time for the $\tt{F500}$ and $\tt{F1000}$ runs 
(blue and orange, respectively) to show the dependence on rotation rate. {\color{blue}In 
\citet{flame_wave1}, we 
used linear least-squares fits to our position vs.\ time data to estimate the propagation velocity. 
For this study we instead fit a quadratic curve to each set of data, as some of the hotter 500~Hz 
runs exhibit significant acceleration. We discard the data points with $t \lesssim 20~\mathrm{ms}$, 
since these correspond to the initial transient period before the flame has begun to propagate 
steadily.} The fit parameters yield estimates of the flame acceleration and velocity at $t = 0$, 
which are provided in Table~\ref{table:flame_speeds}. {\color{blue}Note that the listed velocity is 
only 
a parameter that may be used to calculate the flame speed at an arbitrary time. It is not an 
estimate of the true initial velocity of the flame, since the flame has not achieved ignition yet 
at $t = 0$.} \MarginPar{KE: Outside of updating the data in the table, is there anything else we 
want to add to this para?}

@@

The method for measuring flame propagation described in Section \ref{ssec:rot_propagation} is applied in Figure \ref{fig:flame_speeds_2} to the three 500 Hz runs with $T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$. Due to the lack of a clear burning front in $\tt{F500\_4E8}$, we do not analyze its propagation speed and acceleration. As the initial $T_{\mathrm{star}}$ is increased, the flame becomes greatly accelerated. The initial flame velocities and accelerations derived from a quadratic least-squares fit to each of the datasets are provided in Table~\ref{table:flame_speeds}. The reason for the acceleration of the flame over time is not entirely clear. It could be that energy released from burning begins to dominate the flame's propagation as it evolves, increasing the flame speed over time. Another possibility is that the increased temperatures lead to enhanced turbulent mixing effects that pull in more fresh fuel for the flame to burn. Yet another possibility is that the higher initial $T_{\mathrm{star}}$ leads to a greater average temperature in the fuel layer over time, making it easier for the flame to burn the fuel and propagate.

\begin{figure}[t]
	\centering
	\plotone{500Hz_stacked_enuc1_2order.pdf}
	\caption{\label{fig:flame_speeds_2} Flame front position vs.\ time for the three 500 Hz runs with
		$T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$. The dashed lines show quadratic least-squares fits to the data
		for $t \gtrsim 20~\mathrm{ms}$. Note that due to its rapid acceleration, $\tt{F500\_3E8}$ 
		(orange) is only run out to $\sim 70~\mathrm{ms}$ to avoid surpassing the domain boundary.}
\end{figure}

>>>>

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:flame_speeds} Flame speed and acceleration values measured for each 
	simulation. {\color{blue}$v_0$} is the flame velocity {\color{blue}in the $+r$ direction} at $t 
	= 0$. The initial flame 
	velocities and accelerations are derived from a quadratic least-squares fit to each of the 
	datasets for times $t \gtrsim 20~\mathrm{ms}$. {\color{blue} Using these fit parameters we calculate the velocity at $t = 50~\mathrm{ms}$ ($v_{50}$), at which point the flames have reached steady propagation.}}
	\tablehead{\colhead{run} & \colhead{$v_0$ (cm s$^{-1}$)} & \colhead{$a$ (cm s$^{-2}$)} & \colhead{$v_{50}$ (cm s$^{-1}$)}} 
	\startdata
  {\tt F1000}     & $(3.414 \pm 0.008) \times 10^5$ & $(-1.03 \pm 0.13) \times 10^5$ & $(3.362 \pm 0.010) \times 10^5$\\
  {\tt F500}      & $(3.077 \pm 0.013) \times 10^5$ & $(5.41 \pm 0.19) \times 10^5$ & $(3.347 \pm 0.016) \times 10^5$\\
  {\tt F500\_2E8} & $(3.760 \pm 0.015) \times 10^5$ & $(1.74 \pm 0.25) \times 10^5$ & $(3.847 \pm 0.020) \times 10^5$\\
  {\tt F500\_3E8} & $(-5.293 \pm 0.100) \times 10^5$ & $(3.57 \pm 0.02) \times 10^7$ & $(1.258 \pm 0.015) \times 10^6$\\
	\enddata
	%
\end{deluxetable}

@@

Figure~\ref{fig:flame_speeds_1} gives position vs.\ time for the $\tt{F500}$ and $\tt{F1000}$ runs 
(blue and orange, respectively) to show the dependence on rotation rate. {\color{blue}In 
\citet{flame_wave1}, we 
used linear least-squares fits to our position vs.\ time data to estimate the propagation velocity. 
For this study we instead fit a quadratic curve to each set of data, as some of the hotter 500~Hz 
runs exhibit significant acceleration. We discard the data points with $t \lesssim 20~\mathrm{ms}$, 
since these correspond to the initial transient period before the flame has begun to propagate 
steadily.} The fit parameters yield estimates of the flame acceleration and velocity at $t = 0$, 
which are provided in Table~\ref{table:flame_speeds}. {\color{blue}Note that the listed velocity is 
only 
a parameter that may be used to calculate the flame speed at an arbitrary time. It is not an 
estimate of the true initial velocity of the flame, since the flame has not achieved ignition yet 
at $t = 0$. We use the fit parameters to calculate the flame speeds at $t = 50~\mathrm{ms}$ (when the flame has reached steady propagation), given in the fourth column of Table \ref{table:flame_speeds}.} \MarginPar{KE: Outside of updating the data in the table, is there anything else we 
want to add to this para?}

@@

The method for measuring flame propagation described in Section \ref{ssec:rot_propagation} is applied in Figure \ref{fig:flame_speeds_2} to the three 500 Hz runs with $T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$. Due to the lack of a clear burning front in $\tt{F500\_4E8}$, we do not analyze its propagation speed and acceleration. As the initial $T_{\mathrm{star}}$ is increased, the flame becomes greatly accelerated. The initial flame velocities and accelerations derived from a quadratic least-squares fit to each of the datasets, {\color{blue} as well as the flame velocities at $t = 50~\mathrm{ms}$ calculated using the fit parameters,} are provided in Table~\ref{table:flame_speeds}. {\color{blue} Comparing the flame propagation at different initial temperatures, the most robust feature is the acceleration of the $\tt{F500\_3E8}$ run at $t \sim 40~\mathrm{ms}$.} The reason for the acceleration of the flame over time is not entirely clear. It could be that energy released from burning begins to dominate the flame's propagation as it evolves, increasing the flame speed over time. Another possibility is that the increased temperatures lead to enhanced turbulent mixing effects that pull in more fresh fuel for the flame to burn. Yet another possibility is that the higher initial $T_{\mathrm{star}}$ leads to a greater average temperature in the fuel layer over time, making it easier for the flame to burn the fuel and propagate.

\begin{figure}[t]
	\centering
	\plotone{500Hz_stacked_enuc1_2order.pdf}
	\caption{\label{fig:flame_speeds_2} Flame front position vs.\ time for the three 500 Hz runs with
		$T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$. The dashed lines show quadratic least-squares fits to the data
		for $t \gtrsim 20~\mathrm{ms}$. Note that due to its rapid acceleration, $\tt{F500\_3E8}$ 
		(green) is only run out to $\sim 70~\mathrm{ms}$ to avoid surpassing the domain boundary.}
\end{figure}
